---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
knitr::knit_hooks$set(crop = knitr::hook_pdfcrop)
library(ggplot2)
library(tidyr)
```

# paper

<!-- badges: start -->
<!-- badges: end -->

The goal of paper is to produce summary of publication profile of a scientist or a paper.

## Installation

You can install the released version of paper from [CRAN](https://CRAN.R-project.org) with:

```{r}
# install.packages("paper")
# not yet
```

And the development version from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
# devtools::install_github("kklot/paper")
library(paper)
```
## Example

This is a basic example which shows you how to solve a common problem:

Get all citations to a paper, number of citations to each of those paper, year, and field of study.

```{r example}
ex_paper <- a_paper()
ex_paper
```

Example citation profile of a single paper. The extra margin is cropped with `pdfcrop`, see [document](https://bookdown.org/yihui/rmarkdown-cookbook/crop-plot.html) here.

```{r, crop = TRUE, width = 3, height = 3}
plot(ex_paper)
```